Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-10-10 ms/main.tex
Add equations for invasion

Cooperation and defection can coexist stably at frequencies $\tilde{p}^*$ and $1-\tilde{p}^*$ (\autoref{eq:vert_hori_equilibrium}) if there is horizontal transmission bias for defection, $T_A<T_B$, and the cost of cooperation is intermediate, $\gamma_2 < c < \gamma_1$; see yellow area in \autoref{fig:result2}b.
When unstable coexistence occurs, phenotype $A$ will fix if its initial frequency is $p>\tilde{p}^*$, and phenotype $B$ will fix if its initial frequency is $1-p>1-\tilde{p}^*$; this occurs when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
\autoref{fig:coexistence_without_oblique} shows the mapping $\tilde p \to \tilde p'$; see blue areas in \autoref{fig:result2}a and \autoref{fig:result2}b.
\\

@@

@@

If $p<p^*=1$, we want a condition for $1-p' < 1-p$, or
$\frac{1-p'}{1-p}<1$, or
$\lambda \frac{-(p'-p)}{1-p} < 0$, or
$-\frac{f(p)}{1-p} < 0$.
Using a linear approximation for $f(p)$ near $1$, we have
\begin{equation}\begin{aligned}
1-p' &< 1-p  \Leftrightarrow \\
\frac{f'(1)(p-1) + O\big((p-1)^2\big)}{p-1} &< 0 \Leftrightarrow \\
f'(1) - O(1-p) &< 0.
\end{aligned}\end{equation}
Therefore, if $f'(1)<0$ then there exists $\epsilon>0$ such that for any $1-\epsilon<1-p<1$ we have $1-p'<1-p$; that is, $p'$ is closer to one than $p$.
\end{appendices}

@@

%%% Figure: coexistence map - without oblique transmission
\begin{figure}[h]
\centering
\includegraphics[scale = 0.55]{coexistence_without_oblique.pdf}
\caption{\textbf{Stable and unstable coexistence between cooperation and defection without oblique transmission.}
  The curves show the frequency of the cooperative phenotype $A$ among parents in the next generation, $\tilde{p}'$, vs.\ that in the current generation $\tilde{p}$ (\autoref{eq:nextgen_parents_vertical_only}).
  The dashed black line is $\tilde{p}'=\tilde{p}$.
  The curves and the dashed line intersect at the polymorphic equilibrium $\tilde{p}^*$ (black circle).
  When the curves are above the dashed line, $\tilde{p}'>\tilde{p}$, and $\tilde{p}$ increases.
  When the curves are below the dashed line, $\tilde{p}'<\tilde{p}$, and $\tilde{p}$ decreases.
  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.
  In both cases there is no oblique transmission, $v=1$; see \autoref{fig:coexistence_with_oblique} for $v<1$.
  }
\label{fig:coexistence_without_oblique}
\end{figure}

@@

%%% Figure: coexistence map - with oblique transmission
\begin{figure}[h]
  \centering
  \includegraphics[scale=0.55]{coexistence_with_oblique.pdf}
  \caption{\textbf{Stable and unstable coexistence between cooperation and defection with oblique transmission.}
  The curves show the frequency $\hat{p}'$ of the cooperative phenotype $A$ among juveniles in the next generation vs. that in current generation $\hat{p}$ (\autoref{eq:horizontal}).
  The dashed black line is $\hat{p}'=\hat{p}$.
  The curves and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (black circle).
  When $\hat{p} < \hat{p}^*$ the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
  When $\hat{p} > \hat{p}^*$ the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.
  The orange curve is parameterized by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
  The blue curve is parameterized by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $alpha = 0.09$ and $v=0.6$, which give $\beta_1<\beta_3<0$.
  }
  \label{fig:coexistence_with_oblique}
  \end{figure}

%%% Figure: frequency dynamics
\begin{figure}[h]
  \centering
    \includegraphics[scale=0.7]{Time_Figure_Equal_Horizontal.pdf}
    \includegraphics[scale=0.7]{Time_Figure_Only_Vertical_No_Alpha.pdf}
    \includegraphics[scale=0.7]{Time_Figure_No_Vertical.pdf}
  \caption{
  \textbf{Dynamics of the frequency of cooperation.}
  The frequency $\tilde{p}$ of parents with cooperative phenotype $A$ in \textbf{(a-b)} and the frequency $p$ of adults with cooperative phenotype $A$ in \textbf{(c)}.
  The different lines correspond to parameter values that lead to fixation of cooperation (green), extinction of cooperation (red), or stable coexistence of cooperators and defectors (yellow).
  \textbf{(a)} $v=1$, $T_A=T_B=T = 0.2$, $\alpha = 0.5 \neq 0$, $\tilde{p}_0 = 0.5$ and $c=0.1$; \textbf{(b)} $v=1$, $\alpha = 0$, $\tilde{p}^* \approx 0.35$, $T_A = 0.65$, $T_B = 0.1$, $b=1.3$ and $c=0.65$; \textbf{(c)} $v=0$, $\alpha =0.5$, $p_0 = 0.5$, $T_A = 0.5$, $b=1.3$ and $c = 0.5$.
  }
  \label{fig:results}
\end{figure}

%%% Figure: Spatial model - global selection
\begin{figure}[h]
  \centering
   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection}.pdf}
    ~
    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection}.pdf} \\
  \caption{
  \textbf{Evolution of cooperation in a spatial model.}
  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
  The population evolves on a 100-by-100 grid.
  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in ()\textbf{a}) \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries}.
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
  }
  \label{fig:spatial}
\end{figure}

@@

% Fluctuations in spatial model
\begin{figure}[h]
  \centering
   \includegraphics[scale=0.75]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
   \caption{
    \textbf{Stable coexistence of both phenotypes in spatial model.}
    The dyanmics of the frequancy of cooperators (green) and the frequency of defactors in the spatial model. 
    Both groups has the same initial frequency (0.5) and there are no fixation of one of the groups through the simulation.
    The frequency of cooperators oscillate around the initial frequency. Here, population size is 10,000 (100-by-100 grid), selection operates globally, benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$,
    horizontal transmission of cooperators $T_A = 0.4$, horizontal transmission of defactors $T_B = 0.435$ and cost $c=0.02$.
    }
    \label{fig:spatial_fluctuations}
  \end{figure}
  %TODO: edit this caption. DC

>>>>

Cooperation and defection can coexist stably at frequencies $\tilde{p}^*$ and $1-\tilde{p}^*$ (\autoref{eq:vert_hori_equilibrium}) if there is horizontal transmission bias for defection, $T_A<T_B$, and the cost of cooperation is intermediate, $\gamma_2 < c < \gamma_1$; see yellow area in \autoref{fig:result2}b.
When unstable coexistence occurs, phenotype $A$ will fix if its initial frequency is $p>\tilde{p}^*$, and phenotype $B$ will fix if its initial frequency is $1-p>1-\tilde{p}^*$; this occurs when there is horizontal transmission bias for cooperation, $T_A>T_B$, and the cost is intermediate, $\gamma_1 < c < \gamma_2$.
\autoref{fig:coexistence_recursive}a shows the mapping $\tilde p \to \tilde p'$; see blue areas in \autoref{fig:result2}a and \autoref{fig:result2}b.
\\

@@

\subsection*{Invasion analysis}

In this section we assume perfect vertical transmission and stable coexistence of both cooperates and defector around equilibrium $p^*$.
We saw in result 2 that such situation is possible if there is horizontal bias for defection, $T_B > T_A$ and $\gamma_2 < c < \gamma_1$ 
where c is the cost and $\gamma_1$, $\gamma_2$ is defined in \autoref{eq:cost_boundaries}. The equilibrium $p^*$ is define in \autoref{eq:vert_hori_equilibrium}.

Even though we describe a stable system, in which the frequency of each phenotype does not change, 
it is safe to assume that in reality there are changes that can cause a change in the system parameters. 
For example, a reduction in the cost $c$ that cooperator "pays" for its cooperation will favor cooperation. 
We would like to make invasion analysis for invasion of new kind of individual with different soical association.
For simplicity, we denote the orignal soical association with $\alpha_1$, and the new social association with $\alpha_2$. 
We assume that $\alpha_2 > \alpha_1$.

Before we start the invasion analysis let's examine if mean fitness increases if social association $\alpha$ increases. 
From \autoref{eq:mean_fitness} we know that the mean fitness $\bar{w} = 1 + \hat{p}(b-c)$. In our case $\hat{p} = \hat{p}^*$ the equilibrium.
Therefore, we get that the mean fitness in our scenario is
\begin{equation} \label{eq:mean_fitness_stable_coexistence}
  \bar{w} = 1 + (b-c)\cdot \frac{c(1-T_B) - b \alpha T_A - (T_A-T_B)}{b (1-\alpha) (T_A-T_B)}.
\end{equation} 
We are interested in the sign of derivative $\bar{w}$ by $alpha$ which is the same as the derivative of $\hat{p}^*$ since $b>c$.
\begin{equation} \label{eq:mean_fitness_stable_coexistence_derivative}
  \begin{aligned}
  \frac{d\hat{p}^*}{d\alpha} & =\frac{-b^2T_A (1-\alpha) (T_A-T_B) + b(T_A-T_B)(c(1-T_B) - b \alpha T_A - (T_A-T_B))}{b^2 (1-\alpha)^2 (T_A-T_B)^2} \\
  &= \frac{b^2T_A(T_B-T_A)-bc(1-T_B)(T_B-T_A) - b(T_B-T_A)^2}{b^2 (1-\alpha)^2 (T_A-T_B)^2}
  \end{aligned}
\end{equation} 
Since the denominator is always positive the derivative of mean fitness by alpha will be positive if the numerator is positive for every alpha.
We get the numerator is positive if
\begin{equation} \label{eq:mean_fitness_numerator_condition}
  \begin{aligned}
  &  0 < b^2T_A(T_B-T_A)-bc(1-T_B)(T_B-T_A) - b(T_B-T_A)^2  \\
  & c(1-T_B) < b(T_A-T_B) + (T_A-T_B)  \\
  & c < \frac{b(T_A-T_B) + (T_A-T_B)}{(1-T_B)}.
  \end{aligned}
\end{equation} 
\autoref{eq:mean_fitness_numerator_condition} is always true for stable coexistence because we know from Result2 
that the condition for coexistence is $c<\gamma_1$ and $ \gamma_1 \leq \frac{b(T_A-T_B) + (T_A-T_B)}{(1-T_B)}$. 
Therefore, the mean fitness increases as social association $\alpha$ increases.

In case of invasion we will have 4 types, each type has unique combination of phenotype(A/B) and soical association value ($\alpha_1$/$\alpha_2$).
Let's define their frequencies:
\begin{enumerate}
  \item $\hat{p}_1$ is the frequency of juveniles in next generation with phenotype A and probability of sical association $\alpha_1$
  \item $\hat{p}_2$ is the frequency of juveniles in next generation with phenotype B and probability of sical association $\alpha_1$
  \item $\hat{p}_3$ is the frequency of juveniles in next generation with phenotype A and probability of sical association $\alpha_2$
  \item $\hat{p}_4$ is the frequency of juveniles in next generation with phenotype B and probability of sical association $\alpha_2$
\end{enumerate}

\begin{equation} \label{eq:next_gen_p_1}
  \begin{aligned}
  \bar{w}\hat{p}_1' & = \hat{p}_1(\hat{p}_1+\hat{p_3})(1+b-c)(1 - (1-\alpha_1)(\hat{p}_2 + \hat{p}_4)T_B) \\
  &+ \hat{p}_1(\hat{p}_2 + \hat{p}_4)(1-c)(1-\alpha_1T_B(\hat{p_1}+\hat{p}_3) - T_B(\hat{p}_2+\hat{p}_4)) \\
  &+ \hat{p}_2(\hat{p}_1 + \hat{p}_3)(1+b)T_A(\hat{p}_1 + \hat{p}_3 + \alpha_1(\hat{p}_2 + \hat{p_4})) \\
  &+ \hat{p}_2(\hat{p}_2 + \hat{p}_4)(\hat{p}_1 + \hat{p}_3)(1-\alpha_1)T_A 
  \end{aligned}
\end{equation}
Where the mean fitness $\bar{w} = 1 + (b-c)\cdot(\hat{p}_1 + \hat{p}_3)$. The equations describing $\hat{p}_2'$, $\hat{p}_3'$, $\hat{p}_4'$ is in \autoref{sec:appendixC}.

@@

If $p<p^*=1$, we want a condition for $1-p' < 1-p$, or
$\frac{1-p'}{1-p}<1$, or
$\lambda \frac{-(p'-p)}{1-p} < 0$, or
$-\frac{f(p)}{1-p} < 0$.
Using a linear approximation for $f(p)$ near $1$, we have
\begin{equation}\begin{aligned}
1-p' &< 1-p  \Leftrightarrow \\
\frac{f'(1)(p-1) + O\big((p-1)^2\big)}{p-1} &< 0 \Leftrightarrow \\
f'(1) - O(1-p) &< 0.
\end{aligned}\end{equation}
Therefore, if $f'(1)<0$ then there exists $\epsilon>0$ such that for any $1-\epsilon<1-p<1$ we have $1-p'<1-p$; that is, $p'$ is closer to one than $p$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{} \label{sec:appendixC}

\begin{equation} \label{eq:next_gen_p_2}
  \begin{aligned}
  \bar{w}\hat{p}_2' & = \hat{p}_2(\hat{p}_2+\hat{p_4})(1 - (1-\alpha_1)(\hat{p}_1 + \hat{p}_3)T_A) \\
  &+ \hat{p}_2(\hat{p}_1 + \hat{p}_3)(1+b)(1-\alpha_1T_A(\hat{p}_2 + \hat{p}_4)-T_A(\hat{p}_1 + \hat{p}_3))\\
  &+ \hat{p}_1(\hat{p}_2 + \hat{p}_4)(1-c)(\alpha_1T_B + (1-\alpha_1)(\hat{p}_2+\hat{p}_4)T_B) \\
  &+ \hat{p}_1(\hat{p}_1 + \hat{p}_3)(1-\alpha_1)(\hat{p}_2+\hat{p}_4)T_B 
  \end{aligned}
\end{equation}

\begin{equation} \label{eq:next_gen_p_3}
  \begin{aligned}
  \bar{w}\hat{p}_3' & = \hat{p}_3(\hat{p}_1+\hat{p_3})(1+b-c)(1 - (1-\alpha_2)(\hat{p}_2 + \hat{p}_4)T_B) \\
  &+ \hat{p}_3(\hat{p}_2 + \hat{p}_4)(1-c)(1-\alpha_2T_B(\hat{p_1}+\hat{p}_3) - T_B(\hat{p}_2+\hat{p}_4)) \\
  &+ \hat{p}_4(\hat{p}_1 + \hat{p}_3)(1+b)T_A(\hat{p}_1 + \hat{p}_3 + \alpha_2(\hat{p}_2 + \hat{p_4})) \\
  &+ \hat{p}_4(\hat{p}_2 + \hat{p}_4)(\hat{p}_1 + \hat{p}_3)(1-\alpha_2)T_A 
  \end{aligned}
\end{equation}

\begin{equation} \label{eq:next_gen_p_4}
  \begin{aligned}
  \bar{w}\hat{p}_4' & = \hat{p}_4(\hat{p}_2+\hat{p_4})(1 - (1-\alpha_2)(\hat{p}_1 + \hat{p}_3)T_A) \\
  &+ \hat{p}_4(\hat{p}_1 + \hat{p}_3)(1+b)(1-\alpha_2T_A(\hat{p}_2 + \hat{p}_4)-T_A(\hat{p}_1 + \hat{p}_3))\\
  &+ \hat{p}_3(\hat{p}_2 + \hat{p}_4)(1-c)(\alpha_2T_B + (1-\alpha_2)(\hat{p}_2+\hat{p}_4)T_B) \\
  &+ \hat{p}_3(\hat{p}_1 + \hat{p}_3)(1-\alpha_2)(\hat{p}_2+\hat{p}_4)T_B 
  \end{aligned}
\end{equation}

\end{appendices}

@@

@@

%%% Figure: coexistence map
\begin{figure}[h]
  \centering
    \includegraphics[scale=0.45]{coexistence_without_oblique.pdf}~
    \includegraphics[scale=0.45]{coexistence_with_oblique.pdf}
  \caption{\textbf{Stable and unstable coexistence between cooperation and defection.}
  The curves show the frequency $\hat{p}'$ of the cooperative phenotype $A$ among juveniles in the next generation vs. that in current generation $\hat{p}$ (\autoref{eq:horizontal}).
  The dashed black line is $\hat{p}'=\hat{p}$.
  The curves and the dashed line intersect at the stable equilibrium $\hat{p}^*$ (black circle).
  When $\hat{p} < \hat{p}^*$ the curve is above the dashed line, $\hat{p}' > \hat{p}$, and $\hat{p}$ increases towards $\hat{p}^*$.
  When $\hat{p} > \hat{p}^*$ the curve is below the dashed line, $\hat{p}' < \hat{p}$, and $\hat{p}$ decreases towards $\hat{p}^*$.\\
  \textbf{(a)} There is no oblique transmission, $v=1$.
  The orange curve, for which the polymorphic equilibrium is stable, is given by $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, and $\alpha = 0.45$, which give $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries}).
  The blue curve, for which the equilibrium is unstable, is given by $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, and $\alpha = 0.4$, which give $\gamma_1<c<\gamma_2$.\\
  \textbf{(b)} Oblique transmission exists. 
  The orange curve is parameterized by $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, and $v=0.4$, which give $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients}).
  The blue curve is parameterized by $T_A = 0.5$, $T_B = 0.4$, $b=1.2$, $c=0.487$, $\alpha = 0.09$ and $v=0.6$, which give $\beta_1<\beta_3<0$.
  }
  \label{fig:coexistence_recursive}
  \end{figure}

%%% Figure: frequency dynamics
\begin{figure}[h]
  \centering
    \includegraphics[scale=0.45]{Time_Figure_Equal_Horizontal.pdf}
    ~\\
    \includegraphics[scale=0.45]{Time_Figure_Only_Vertical_No_Alpha.pdf}
    ~\\
    \includegraphics[scale=0.45]{Time_Figure_No_Vertical.pdf}
  \caption{
  \textbf{Dynamics of the frequency of cooperation.}
  The frequency $\tilde{p}$ of parents with cooperative phenotype $A$ in \textbf{(a-b)} and the frequency $p$ of adults with cooperative phenotype $A$ in \textbf{(c)}.
  The different lines correspond to parameter values that lead to fixation of cooperation (green), extinction of cooperation (red), or stable coexistence of cooperators and defectors (yellow).
  \textbf{(a)} $v=1$, $T_A=T_B=T = 0.2$, $\alpha = 0.5 \neq 0$, $\tilde{p}_0 = 0.5$ and $c=0.1$; \textbf{(b)} $v=1$, $\alpha = 0$, $\tilde{p}^* \approx 0.35$, $T_A = 0.65$, $T_B = 0.1$, $b=1.3$ and $c=0.65$; \textbf{(c)} $v=0$, $\alpha =0.5$, $p_0 = 0.5$, $T_A = 0.5$, $b=1.3$ and $c = 0.5$.
  }
  \label{fig:results}
\end{figure}

%%% Figure: Spatial model - global selection
\begin{figure}[h]
  \centering
   \includegraphics[scale=0.5]{{Ta=Tb_b=1.3_globalSelection}.pdf}
    ~
    \includegraphics[scale=0.5]{{Ta=0.4_Tb=0.3-0.5_b=1.3_globalSelection}.pdf} \\
  \caption{
  \textbf{Evolution of cooperation in a spatial model.}
  The expected frequency of cooperators in a structured population after 10,000 generations is shown (red for 0\%, green for 100\%) as function of both the cost of cooperation ($c$) on the y-axis, and the symmetric horizontal transmission rate ($T=T_A=T_B$) on the x-axis of the left panel, or the transmission bias $T_A-T_B$ on the x-axis of the right panel.
  The population evolves on a 100-by-100 grid.
  Cooperation and horizontal transmission are both local between adjacent sites, and each site had 8 neighbors.
  Selection operates globally (see \autoref{fig:spatial_local_selection} for results from a model with local selection).
  The black curves represent the cost boundaries for the evolution of cooperation in a well-mixed population with social association where $\alpha=1/8$ in \textbf{(a)} \autoref{eq:equal_transmission} and \textbf{(b)} \autoref{eq:cost_boundaries}.
  Simulations were stopped at generation 10,000 or if one of the phenotypes fixed and 50 simulations were executed for each parameter set.
  Here, population size is 10,000 (100-by-100 grid), benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$.
  \textbf{(a)} Symmetric horizontal transmission, $T=T_A=T_B$.
  \textbf{(b)} Horizontal transmission rates $T_A=0.4$, $0.3<T_B<0.5$.
  }
  \label{fig:spatial}
\end{figure}

@@

% Fluctuations in spatial model
\begin{figure}[h]
  \centering
   \includegraphics[scale=0.75]{{timeSereis_b=1.3_TA=0.4_TB=0.435_c=0.02_globalSelection_normalizeByNumInteractions}.pdf}
   \caption{
    \textbf{Stable coexistence of both phenotypes in spatial model.}
    The frequancy of cooperators (green) and defactors (red) in the spatial model. 
    Both phenotypes have initial frequency of 50 precent. The figure shows that there are no fixation of nither phenotype through out the simulation.
    The frequency of both cooperators and defactors oscillates around the initial frequency. Here, population size is 10,000 (100-by-100 grid), selection operates globally, 
    benefit of cooperation, $b=1.3$, perfect vertical transmission $v=1$, horizontal transmission of cooperators $T_A = 0.4$, horizontal transmission of defactors $T_B = 0.435$ and cost $c=0.02$.
    }
    \label{fig:spatial_fluctuations}
  \end{figure}
  %TODO: edit this caption. DC
